---
title: "Exploratory data analysis"
author: "Cecile Murray"
date: "4/19/2020"
output: html_document
---

```{r setup, include=FALSE}
setwd("~/Documents/CAPP/CAPP-30255/cfpb-complaints/explore")

libs <- c("here",
          "tidyverse",
          "magrittr",
          "purrr",
          "knitr", 
          "kableExtra",
          "janitor")
lapply(libs, library, character.only = TRUE)

set_here()
```

```{r loading, results='hide'}
# load in data
raw <- read_csv("../data/complaints.csv")

# filter to only complaints with text 
complaints <- raw %>% 
  clean_names() %>% 
  filter(!is.na(consumer_complaint_narrative),
         consumer_complaint_narrative != "")
```

```{r xtabs}

# some crosstabs - looking good on missing values, generally
complaints %>% 
  tabyl(consumer_consent_provided) %>%
  mutate(percent = scales::number(percent, accuracy = 0.01))
complaints %>%
  tabyl(company_response_to_consumer) %>%
  mutate(percent = scales::number(percent, accuracy = 0.01))
complaints %>% 
  tabyl(company_public_response) %>%
  mutate(percent = scales::number(percent, accuracy = 0.01)) 

complaints %>% tabyl(company_public_response,
                     company_response_to_consumer)
```

Florida appears to be disproportionately represented

```{r st_xtab}
# how many states does this affect?
complaints %>% 
  tabyl(state) %>% 
  mutate(percent = scales::number(percent, accuracy = 0.01))
```

4,500 unique companies (without efforts to check for dups). And about 1/3 of complaints are about credit reporting.

```{r companies}
# number of unique companies: 4500
length(unique(complaints$company))

# mostly people are complaining about credit bureaus (30% of complaints)
complaints %>% 
  tabyl(company) %>% 
  mutate(percent = scales::number(percent, accuracy = 0.01)) %>% 
  arrange(-n) 

# specifically credit reporting is the issue
complaints %>%
  tabyl(sub_product) %>% 
  mutate(percent = scales::number(percent, accuracy = 0.01)) %>% 
  arrange(-n)
```

Timeline of data: # of complaints has actually tanked... reporting issue?
According to the website, "[c]omplaints are published after the company responds, confirming a commercial relationship with the consumer, or after 15 days, whichever comes first."

```{r complaint_time_chart}
complaints %>% 
  ggplot(aes(x = date_received)) +
  geom_freqpoly()
```

Note also what we don't see in this database: "[c]omplaints referred to other regulators, such as complaints about depository institutions with less than $10 billion in assets, are not published in the Consumer Complaint Database."

^I think this means every company in here should be in FDIC databases, based on size?

```{r complaint_trends}
complaints %>% 
  ggplot(aes(x = date_received,
             fill = product)) +
  geom_area(stat = "density") +
  theme(legend.position = "bottom")
```
